Quantum Hoare Type Theory

### 2020-04-29 ms-paper/ms-paper.tex
Add bibentry for Fu, Kishida, Selinger paper on Linear Dependent Type Theory

\paragraph{Linearity} Peter Selinger and collaborators have recently proposed a linear dependent typed version of Proto-Quipper (dubbed Proto-Quipper-D)~\cite{selinger2020}. It is an interesting challenge to reconcile linearity in our theory based on their proposal.

>>>>

\paragraph{Linearity} Peter Selinger and collaborators have recently proposed a linear dependent typed version of Proto-Quipper (dubbed Proto-Quipper-D)~\cite{selinger2020,fu2020linear}. It is an interesting challenge to reconcile linearity in our theory based on their proposal.
